Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-10 documentation/paper.tex
Included table of results for waveform without wall cuts

Two different configurations were tested:
\begin{enumerate}
    \item A configuration that operates strictly on $\omega$ with no position corrections of any kind (furthermore $DeepConv(\omega)$).
    \item A configuration with an additional position input on a lower layer such that it should be able to learn to incorporate position corrections into its outputs ($DeepConvWithPos(\omega, \chi)$).
\end{enumerate}

@@

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), $DeepConvWithPos(\omega, \chi)$ achieved 85\%. The maximum obtained on a grid search with position input was 91\% (although with a high class-wise standard deviation of 0.61). While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

However, the lack of decisiveness observed even when accuracy was relatively high, as seen in Figure \ref{waveform_best_validation}, implies this is a suboptimal technique.

@@

>>>>

Two different configurations were tested:
\begin{enumerate}
    \item A configuration that operates strictly on $\omega$ with no position corrections of any kind (furthermore $DeepConv(\omega)$).
    \item A configuration with an additional position input on a lower layer such that it should be able to learn to incorporate position corrections into its outputs ($DeepConvWithPos(\omega, \chi)$). This configuration was tested both with and without $WallCut(D)$.
\end{enumerate}

@@

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), and still without $WallCut(D)$, $DeepConvWithPos(\omega, \chi)$ achieved 85\%. The maximum obtained on a grid search with this configuration was 91\% (although with a high class-wise standard deviation of 0.61). While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

However, the lack of decisiveness observed even when accuracy was relatively high, as seen in Figure \ref{waveform_best_validation}, implies that without $WallCut(D)$, this is a suboptimal technique.

@@

!!!Include results with wall cuts!!!

The following tables show the results of several $DeepConvWithPos(\omega, \chi)$ discriminators produced throughout testing, with corresponding network hyperparameters.

!!!TODO!!!

\begin{tabular}{|l|l|l|l|l|l|l|}
    \hline
    L2 $\lambda$ & Dropout & Filters & Kernel Size & \# Layers Multiplier & Max Accuracy & Class-Wise Std Dev \\
    \hline
    0.003 & 0 & 24 & 3 & 3 & 91\% & 0.61 \\
    \hline
    0.003 & 0.5 & 24 & 5 & 3 & 91\% & 0.65 \\
    \hline
    0.001 & 0.25 & 24 & 3 & 3 & 91\% & 0.66 \\
    \hline
    0.001 & 0.5 & 48 & 5 & 3 & 88\% & 0.73 \\
    \hline
    0.0003 & 0 & 48 & 5 & 6 & 78\% & 0.95 \\
    \hline
    0.0003 & 0.5 & 48 & 5 & 6 & 74\% & 0.92 \\
    \hline
\end{tabular}
